### 2019-07-10 thesis.tex
*** empty log message ***

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and technically infinite energy source
when scientists and engineers manage to succeed at obtaining a controlled, and
energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
everyday life are rare, restricted to the occurrence of lightning during storms,
flames, and the beautiful auroras that take place at high latitudes. In the
interplanetary and interstellar space, however, the situation is the opposite.
Starting in the outer layers of Earth's atmosphere, passing through the solar
wind in the interplanetary space, to the stellar interiors and atmospheres,
accretion disks, and molecular clouds it is estimated that something around
$99 \sim 99.9\%$ of the observable matter is in the plasma state \cite{may}. 
Therefore, the study and comprehension of the physics of plasma processes is a
fundamental branch of astrophysics.

The

>>>>

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to
the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
research laboratories, and the promise of cleaner and technically infinite
energy source when scientists and engineers manage to succeed at obtaining
a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
Naturally occurring plasmas in our everyday life are rare, restricted to the
occurrence of lightning during storms, flames, and the beautiful auroras that
take place at high latitudes. In the interplanetary and interstellar space,
however, the situation is the opposite. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
is in the plasma state \cite{may}. Therefore, the study and comprehension of
the physics of plasma processes is a fundamental branch of astrophysics.

Plasma is a gas in which the atoms -or molecules- are in an ionized state.
In such condition, long-range electric and magnetic forces determine the
interactions of the charged particles. This coupling between the variations
in the electric and magnetic fields and the motion of ions and electrons
gives rise to the myriad of collective processes that characterize a
plasma\cite{tsytotp}.
